---
title: "Tidy FAO Production data"
author: "Danielle Ferraro, UC Santa Barbara"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
    number_sections: true
---

# Introduction

This document describes the methods used to tidy FAO production data (capture and aquaculture) for use in Track 1 of the Brewfish project.

The major operations performed on the data are:

- Filter out quantities of taxa recorded as individuals (whales, crocodiles/alligators/seals)
- Transform neglgibles
- Add sector column
- Add country metadata 
- Clean column names

**Input:** Raw FAO production - `TS_FI_PRODUCTION.csv`.  
**Output:** Tidied FAO production - `fao_production_tidy.csv`.

# Setup

Install packages.
```{r packages, message = FALSE}
library(here)
library(tidyverse)
library(janitor)
```

Source scripts. 
```{r scripts, eval = TRUE}
source(here("src", "directories.R"))
```

# Import data

```{r import-production-data, message = FALSE}
# FAO Production 
production <- read_csv(file.path(dir_raw_data, "FAO", "production", "TS_FI_PRODUCTION.csv"), 
                       col_types = cols(UNIT = col_character())) %>% 
  clean_names()
# FAO country metadata
country_key <- read_csv(file.path(dir_raw_data, "FAO", "production", "CL_FI_COUNTRY_GROUPS.csv")) %>% 
  clean_names()
# Master species key
master_spp_key <- read_csv(file.path(dir_data_aquaculture, "keys", "master_species_key.csv"))
```

# Tidy data

Append country names to production data. 

```{r append-country-names}
production <- production %>% 
  left_join(country_key[,c("un_code", "name_en", "eco_class_group")], by = c("country" = "un_code")) %>% 
  rename(country_name = name_en)
```

Evaluate symbols. According to the FAO metadata (also available on NCEAS' Aurora server at `r file.path(dir_raw_data, "FAO", "production", "CL_FI_SYMBOL.csv")`), the different characters in the `SYMBOL` column correspond to the following notes:

Code|Symbol|Name|Description
-----|-----|-----|-----
1|.|UNKNOWN|Data not available; unobtainable; data not separately available but included in another category
2|0|NEGLIGIBLE|More than zero but less than half the unit used
3|-|ZERO|None; magnitude known to be nil or zero
4|F|ESTIMATED|FAO estimate from available sources of information or calculation based on specific assumptions
5|R|REPETITION|Repetition
6| |OFFICIAL|Official Data

```{r transform-symbols}
table(production$symbol) # Need to transform the negligibles (symbol == "0") and zeroes (symbol == "-")
production <- production %>% 
  mutate(quantity = case_when(symbol=="0" ~ 0.5,
                              symbol=="-" ~ 0,
                              TRUE ~ quantity))
```

Identify aquaculture vs. capture landings. According to the FAO metadata (also available on NCEAS' Aurora server at `r file.path(dir_raw_data, "FAO", "production", "CL_FI_PRODUCTION_SOURCE.csv")`), the different numbers in the `SOURCE` column correspond to the following types of production:

Identifier|Code|Name
-----|-----|-----
5|AQUACULTURE|Aquaculture production
1|FRESHWATER|Aquaculture production (freshwater)
2|BRACKISHWATER|Aquaculture production (brackishwater)
3|MARINE|Aquaculture production (marine)
4|CAPTURE|Capture production

```{r define-sector}
production <- production %>% 
  mutate(sector = if_else(source==4, "Capture", "Aquaculture"))
```

Identify landings recorded as the number of individuals instead of tonnage. According to the FAO metadata (also available on NCEAS' Aurora server at `r file.path(dir_raw_data, "FAO", "production", "CL_FI_UNIT.csv")`), the different characters in the `UNIT` column correspond to the following units:

Code|Name_En
-----|-----
n3|Quantity (number 1000)
t|Quantity (tonnes)
v|Value (USD 1000)
no|Quantity (number)
h|Effort (hours)
kg|Quantity (kilograms)
m|Length (meters)

All landings are reported in metric tons, except for whales, seals, and crocodiles, which are reported in number of individuals. **Here those landings are removed.**

```{r filter-individuals}
production <- production %>% 
  filter(unit != "no")
```

# Save

```{r save}
write_csv(production, file.path(dir_data_aquaculture, "fao_production_tidy.csv"))
```

